### 2018-07-28 Sections/QTCP_protocol_stack.tex
dB, \text->mathrm

We can express the state of an entire \textsc{Packet} as,
\begin{align}
\hat\rho_\text{packet}(i) = \hat\rho_\text{quantum}(i) \oplus \hat\rho_\text{classical}(i) \oplus \hat\rho_\text{header}(i),
\end{align}
where $i$ denotes the $i$th packet. Here $\hat\rho_\text{quantum}$ ($\hat\rho_\text{classical}$) is a block of \textsc{Quantum Block Size} qubits (\textsc{Classical Block Size} bits) taken from the user's \textsc{Quantum Data} (\textsc{Classical Data}), while $\hat\rho_\text{header}$ is the \textsc{Packet's} classical \textsc{Packet Header}. As discussed earlier, since $\hat\rho_\text{quantum}$ is quantum, and $\hat\rho_\text{classical}$ and $\hat\rho_\text{header}$ are classical, they needn't be transmitted together over the same quantum network. Instead all \textsc{Classical Data} and \textsc{Packet Header} could be transmitted over a classical network operating in parallel to and synchronised with the quantum network, which carries the \textsc{Quantum Data}.

Note that while one can always measure classical data without disturbance, this is not the case with quantum data, where measurements cause wavefunction collapse. Thus, while Alice is always able to know $\hat\rho_\text{classical}$ and $\hat\rho_\text{header}$, she may or may not know $\hat\rho_\text{quantum}$. Clearly if she prepared the state herself, she would (hopefully) know what she was doing. But in general, quantum networks could be used for far less trivial networking, where Alice is, for example, an intermediary in a distributed quantum computation. In this instance, Alice is unlikely to know what her \textsc{Quantum Data} is.

@@

The \textsc{Strategy} layer is responsible for evaluating the net cost function $f_\text{cost}$ from Eq.~(\ref{eq:net_cost_R}), which accounts for both \textsc{Costs} and \textsc{Attributes} to calculate a single effective cost measure that may be employed in routing decisions.

@@

Having communicated all the \textsc{Packet Data} from Alice to Bob, performed \textsc{Reconstruction}, and applied \textsc{QoS} protocols, Bob ought to have $\hat\rho_\text{data}$ to a good approximation. The quality of Bob's received state can be inferred directly from the \textsc{Costs} vector contained in the \textsc{Packet Headers}. The final state and its associated quality metrics (\textsc{Costs} and QEC outcomes) may then be provided to Bob as a software interface for end use.

>>>>

We can express the state of an entire \textsc{Packet} as,
\begin{align}
\hat\rho_\mathrm{packet}(i) = \hat\rho_\mathrm{quantum}(i) \oplus \hat\rho_\mathrm{classical}(i) \oplus \hat\rho_\mathrm{header}(i),
\end{align}
where $i$ denotes the $i$th packet. Here $\hat\rho_\mathrm{quantum}$ ($\hat\rho_\mathrm{classical}$) is a block of \textsc{Quantum Block Size} qubits (\textsc{Classical Block Size} bits) taken from the user's \textsc{Quantum Data} (\textsc{Classical Data}), while $\hat\rho_\mathrm{header}$ is the \textsc{Packet's} classical \textsc{Packet Header}. As discussed earlier, since $\hat\rho_\mathrm{quantum}$ is quantum, and $\hat\rho_\mathrm{classical}$ and $\hat\rho_\mathrm{header}$ are classical, they needn't be transmitted together over the same quantum network. Instead all \textsc{Classical Data} and \textsc{Packet Header} could be transmitted over a classical network operating in parallel to and synchronised with the quantum network, which carries the \textsc{Quantum Data}.

Note that while one can always measure classical data without disturbance, this is not the case with quantum data, where measurements cause wavefunction collapse. Thus, while Alice is always able to know $\hat\rho_\mathrm{classical}$ and $\hat\rho_\mathrm{header}$, she may or may not know $\hat\rho_\mathrm{quantum}$. Clearly if she prepared the state herself, she would (hopefully) know what she was doing. But in general, quantum networks could be used for far less trivial networking, where Alice is, for example, an intermediary in a distributed quantum computation. In this instance, Alice is unlikely to know what her \textsc{Quantum Data} is.

@@

The \textsc{Strategy} layer is responsible for evaluating the net cost function $f_\mathrm{cost}$ from Eq.~(\ref{eq:net_cost_R}), which accounts for both \textsc{Costs} and \textsc{Attributes} to calculate a single effective cost measure that may be employed in routing decisions.

@@

Having communicated all the \textsc{Packet Data} from Alice to Bob, performed \textsc{Reconstruction}, and applied \textsc{QoS} protocols, Bob ought to have $\hat\rho_\mathrm{data}$ to a good approximation. The quality of Bob's received state can be inferred directly from the \textsc{Costs} vector contained in the \textsc{Packet Headers}. The final state and its associated quality metrics (\textsc{Costs} and QEC outcomes) may then be provided to Bob as a software interface for end use.

### 2018-07-28 Sections/cloud_quantum_computing.tex
dB, \text->mathrm

Let $t_c$ be the time required by a classical algorithm to solve a given problem, and $t_q$ the time required to solve the same problem using a quantum algorithm. In the case of algorithms exhibiting exponential quantum speedup, we will have,
\begin{align}
t_c = O(\text{exp}(t_q)).
\end{align}
If we now increase the quantum processing power $k$-fold, the equivalent classical processing time is (in the best case),
\begin{align}
t_c' &= O(\text{exp}(t_q k)) \nonumber \\
&= O(\text{exp}(t_q)^{k}) \nonumber \\
&= O({t_c}^{k}).
\end{align}
Thus, $k$-fold quantum enhancement corresponds to a $k$th-order exponential enhancement in the equivalent classical processing time, which clearly scales much more favourably than the linear $k$-fold enhancement offered by classical parallelisation.

@@

Let us first assume that we wish to construct a cluster state with $n_\text{logical}$ logical qubits. We additionally allow each logical qubit to be the root node of a graph with a $+$-structure, where each branch comprises a chain of $n_\text{ancilla}$ ancillary physical qubits. These are sometimes referred to as \textit{micro-clusters} \cite{bib:Nielsen04}\index{Micro-cluster states}. A single micro-cluster collectively forms a single \textit{module} in the topology. Our goal is to fuse modules via nearest neighbour entanglement to build up the desired distributed cluster state.

@@

When an EO is successful, we have fused two modules together, albeit potentially with some leftover ancillary states between the logical qubits. When it fails, we have lost the respective ancillary states, and we attempt again using the next ancillary qubits in each of the the respective branches -- a kind of \textsc{Repeat Until Success} strategy. The bonding only fails if all $n_\text{ancilla}$ EOs fail.

@@

This approach has been shown to be resource-efficient \cite{bib:YoranReznik03, bib:Nielsen04}. Let us perform a rudimentary analysis of the resource scaling of this type of approach. The probability of successfully creating an edge between two modules is,
\begin{align}
p_\text{success} = 1 - {p_\text{failure}}^{n_\text{ancilla}},
\end{align}
where $p_\text{success}$ is the probability of joining two modules, $p_\text{failure}$ is the probability that a single EO fails, and $n_\text{ancilla}$ is the number of ancillary qubits per chain. $p_\text{success}$ can be made arbitrarily close to unity with sufficiently long ancillary chains, the required length of whom scales as,
\begin{align}
n_\text{ancilla} = \frac{\text{log}(1-p_\text{success})}{\text{log}(p_\text{failure})}.
\end{align}

@@

Let us assume we have a `primary' linear topology of modules, which we will incrementally attempt to `grow' by tacking on new modules to the end. When we do so, with probability $p_\text{success}$ we grow the length of the primary by 1, otherwise we decrement it by 1. This proceeds as a random walk, with on average \mbox{$2p_\text{success}-1$} new qubits added to the primary per time-step. Provided this number is positive, i.e \mbox{$p_\text{success}>1/2$}, which can always be achieved with sufficient $n_\text{ancilla}$, the length of the primary grows linearly over time, allowing efficient state preparation.

>>>>

Let $t_c$ be the time required by a classical algorithm to solve a given problem, and $t_q$ the time required to solve the same problem using a quantum algorithm. In the case of algorithms exhibiting exponential quantum speedup, we will have,
\begin{align}
t_c = O(\mathrm{exp}(t_q)).
\end{align}
If we now increase the quantum processing power $k$-fold, the equivalent classical processing time is (in the best case),
\begin{align}
t_c' &= O(\mathrm{exp}(t_q k)) \nonumber \\
&= O(\mathrm{exp}(t_q)^{k}) \nonumber \\
&= O({t_c}^{k}).
\end{align}
Thus, $k$-fold quantum enhancement corresponds to a $k$th-order exponential enhancement in the equivalent classical processing time, which clearly scales much more favourably than the linear $k$-fold enhancement offered by classical parallelisation.

@@

Let us first assume that we wish to construct a cluster state with $n_\mathrm{logical}$ logical qubits. We additionally allow each logical qubit to be the root node of a graph with a $+$-structure, where each branch comprises a chain of $n_\mathrm{ancilla}$ ancillary physical qubits. These are sometimes referred to as \textit{micro-clusters} \cite{bib:Nielsen04}\index{Micro-cluster states}. A single micro-cluster collectively forms a single \textit{module} in the topology. Our goal is to fuse modules via nearest neighbour entanglement to build up the desired distributed cluster state.

@@

When an EO is successful, we have fused two modules together, albeit potentially with some leftover ancillary states between the logical qubits. When it fails, we have lost the respective ancillary states, and we attempt again using the next ancillary qubits in each of the the respective branches -- a kind of \textsc{Repeat Until Success} strategy. The bonding only fails if all $n_\mathrm{ancilla}$ EOs fail.

@@

This approach has been shown to be resource-efficient \cite{bib:YoranReznik03, bib:Nielsen04}. Let us perform a rudimentary analysis of the resource scaling of this type of approach. The probability of successfully creating an edge between two modules is,
\begin{align}
p_\mathrm{success} = 1 - {p_\mathrm{failure}}^{n_\mathrm{ancilla}},
\end{align}
where $p_\mathrm{success}$ is the probability of joining two modules, $p_\mathrm{failure}$ is the probability that a single EO fails, and $n_\mathrm{ancilla}$ is the number of ancillary qubits per chain. $p_\mathrm{success}$ can be made arbitrarily close to unity with sufficiently long ancillary chains, the required length of whom scales as,
\begin{align}
n_\mathrm{ancilla} = \frac{\mathrm{log}(1-p_\mathrm{success})}{\mathrm{log}(p_\mathrm{failure})}.
\end{align}

@@

Let us assume we have a `primary' linear topology of modules, which we will incrementally attempt to `grow' by tacking on new modules to the end. When we do so, with probability $p_\mathrm{success}$ we grow the length of the primary by 1, otherwise we decrement it by 1. This proceeds as a random walk, with on average \mbox{$2p_\mathrm{success}-1$} new qubits added to the primary per time-step. Provided this number is positive, i.e \mbox{$p_\mathrm{success}>1/2$}, which can always be achieved with sufficient $n_\mathrm{ancilla}$, the length of the primary grows linearly over time, allowing efficient state preparation.

### 2018-07-28 Sections/costs_and_attributes_in_quantum_networks.tex
dB, \text->mathrm

The efficiency measure introduced previously is multiplicative, so for consecutive lossy channels the net efficiency is,
\begin{align}
\eta_\text{net}=\prod_i \eta_i,
\end{align}
where $\eta_i$ is the efficiency of the $i$th channel. Intuitively, this is simply telling us that if a photon passes through a channel with success probability $\eta_1$, followed by another with $\eta_2$, the total success probability is \mbox{$\eta_1\eta_2$}.

When employing single-photon encoding of qubits (e.g using the polarisation degree of freedom), there are three basis states of interest: a single photon horizontally polarised ($\ket{H}$); a single photon vertically polarised ($\ket{V}$); and, the vacuum state ($\ket{0}$). The effect of the loss channel on this type of state is to map $\ket{H}$ and $\ket{V}$ to $\ket{\text{0}}$ with probability \mbox{$1-\eta$}, while doing nothing to $\ket{\text{0}}$. Note that because the loss process affects both logical basis states ($\ket{H}$ and $\ket{V}$) identically, its action is invariant under unitary operations in the logical (i.e polarisation) basis space.

@@

Because spectral filtering can be regarded as a frequency-dependent loss channel, its associated cost can be treated in the same manner, except that rather than keeping track of a single efficiency $\eta$, we track a frequency response function $\eta_f(\omega)$, with the same multiplicative property,
\begin{align}
	\eta_f^\text{(net)}(\omega)=\prod_i \eta_f^{(i)}(\omega).
\end{align}

@@

The dephasing and depolarising channels, given by Eqs.~(\ref{eq:dephasing_channel},\ref{eq:depolarizing_channel}), also behave multiplicatively. If $p_i$ is the probability that the state passing through the $i$th channel in series does not undergo the error process, then the probability of the state passing though the entire series without error is simply,
\begin{align}
p_\text{net}=\prod_i p_i,
\end{align}
exhibiting the same multiplicative behaviour as the loss channel. The same observation applies to any of the other Pauli error channels.

@@

In Sec.~\ref{sec:MM_error} we introduced a simple model for temporal mode-mismatch as a displacement in the temporal wave-function of photons propagating through a channel. Clearly, such a process is cumulative -- a temporal displacement of $\Delta_1$ followed by another of $\Delta_2$ yields a net displacement of \mbox{$\Delta_1+\Delta_2$}. Thus, for a chain of such channels we simply accumulate a net temporal displacement of,
\begin{align}
\Delta_\text{net} = \sum_i \Delta_i.
\end{align}

@@

The fidelity\index{Fidelity} between two states is defined as,
\begin{align}
\mathcal{F}(\hat\rho_1,\hat\rho_2) = \text{tr}\left(\sqrt{\hat\rho_1^{1/2}\cdot\hat\rho_2\cdot\hat\rho_1^{1/2}}\right),
\end{align}
where,
\begin{align}
& \mathcal{F}(\hat\rho_1,\hat\rho_2) = \mathcal{F}(\hat\rho_2,\hat\rho_1), \nonumber \\
& 0\leq \mathcal{F}(\hat\rho_1,\hat\rho_2) \leq 1.
\end{align}
\mbox{$\mathcal{F}(\hat\rho_1,\hat\rho_2)=1$} iff the states are equal, and \mbox{$\mathcal{F}(\hat\rho_1,\hat\rho_2)=0$} iff they are orthogonal.
In the case where one of the states is a pure state, this simplifies to,
\begin{align}
\mathcal{F}(\hat\rho_1,\ket{\psi_2}) = \bra{\psi_2}\hat\rho_1\ket{\psi_2},
\end{align}
and when both states are pure to simply,
\begin{align}
\mathcal{F}(\ket{\psi_1},\ket{\psi_2}) = |\langle\psi_1 | \psi_2\rangle|^2.
\end{align}

@@

We define the fidelity of two processes, the process fidelity \index{Fidelity} \cite{bib:Gilchrist05}, to be the fidelity between two identical copies of a state that have been evolved under each of those processes, minimised over all possible states. That is, it provides a lower bound on the fidelity between identical states evolved under the two processes. In the context of networking, where quality must be guaranteed, this definition is more appropriate than, say, the average case fidelity. Specifically,
\begin{align}
\mathcal{F}(\mathcal{E}_1,\mathcal{E}_2) = \text{tr}\left( \sqrt{\chi_1^{1/2}\cdot\chi_2\cdot\chi_1^{1/2}}\right),
\end{align}
where $\chi_1$ and $\chi_2$ are the process matrices for $\mathcal{E}_1$ and $\mathcal{E}_2$.

@@

The purity of a state that was initially pure quantifies how well quantum coherence was maintained during evolution, equivalently how well superpositions are maintained. The purity is defined as,
\begin{align}
\mathcal{P}(\hat\rho) = \text{tr}(\hat\rho^2),
\end{align}
where,
\begin{align}
\frac{1}{\text{dim}(\hat\rho)} \leq \mathcal{P}(\hat\rho) \leq 1.
\end{align}
We have \mbox{$\mathcal{P}(\hat\rho) = 1$} iff \mbox{$\hat\rho=\ket{\psi}\bra{\psi}$} is a pure state, and \mbox{$\mathcal{P}(\hat\rho)=1/\text{dim}(\hat\rho)$} iff \mbox{$\hat\rho=\mathbb{\hat{I}}/\text{dim}(\hat\rho)$} is the maximally mixed state.

@@

The purity of a process is defined analogously to the fidelity of a process,
\begin{align}
\mathcal{P}(\mathcal{E}) = \text{tr}(\chi^2),
\end{align}
and as with the fidelity, a lower bound on the purity of multiple processes in series is multiplicative,
\begin{align}
\mathcal{P}(\mathcal{E}_2\circ\mathcal{E}_1)
\geq \mathcal{P}(\mathcal{E}_2)\cdot\mathcal{P}(\mathcal{E}_1).
\end{align}
\comment{CHECK THIS!}. If the channel implements a unitary operation then necessarily \mbox{$\mathcal{P}(\mathcal{E})=1$}.

@@

When distributing entanglement between separate nodes, metrics quantifying bipartite entanglement are relevant. For pure bipartite states $\ket{\psi}_{A,B}$, the purity of one of the reduced subsystems directly quantifies the degree of entanglement between them,
\begin{align}
\mathcal{M}(\ket{\psi}_{A,B})) &= \mathcal{P}(\text{tr}_A(\ket{\psi}_{A,B})) \nonumber \\
&= \mathcal{P}(\text{tr}_B(\ket{\psi}_{A,B})),
\end{align}
The entanglement between two systems in invariant under local unitaries,
\begin{align}
\mathcal{M}(\ket{\psi}_{A,B}) = \mathcal{M}([\hat{U}_A\otimes \hat{U}_B]\ket{\psi}_{A,B}).
\end{align}

@@

The Shannon entropy \cite{???} of a classical probability distribution $X$ is given by,
\begin{align}\index{Shannon entropy}
H(X) = -\sum_x p_x\text{log}_2(p_x),
\end{align}
where $p_x$ are the probabilities in the distribution. For a joint distribution over $X$ and $Y$ this simply generalises to,
\begin{align}\index{Joint Shannon entropy}
H(X,Y) =  -\sum_{x,y} p_{x,y}\text{log}_2(p_{x,y})
\end{align}

The von Neuman entropy \cite{???} for quantum density operators, $S(\hat\rho)$, is defined analogously, replacing probabilities with density operator eigenvalues,
\begin{align}\index{von Neuman entropy}
S(\hat\rho) &= - \sum_x \lambda_x \text{log}_2 (\lambda_x) \nonumber \\
&= -\text{tr}(\hat\rho\,\text{log}\,\hat\rho),
\end{align}
where $\{\lambda\}$ is the eigenvalue spectrum of $\hat\rho$. This modification is logically justified, as the eigenvalues can be interpreted directly as a purely classical probability distribution of orthogonal states when the density operator is transformed into a basis with no coherences between basis states (i.e a diagonal basis or spectral decomposition). In that case the Shannon and von Neuman entropies essentially have identical physical interpretations.

@@

In general, for a series of links \mbox{$v_1\to v_2 \to \dots \to v_n$} characterised by multiplicative measure $m$, the equivalent cost metric is,
\begin{align} \label{eq:dist_log}\index{Logarithmic distance}
c_{v_1\to v_2 \to \dots \to v_n} = -\sum_{i=1}^{n-1} \text{log}(m_{v_i\to v_{i+1}}).
\end{align}
We have assumed that \mbox{$0\leq m \leq 1$}, where \mbox{$m=0$} represents complete failure, and \mbox{$m=1$} represents ideal operation.

@@

In the case of mutual information and channel capacity, it makes most sense to consider the number of bits that are lost by a channel, rather than the number communicated, since then we have a measure with quasi-metric properties. Specifically, let the number of bits lost by a channel be the difference between the number of bits in the input state and the channel capacity,
\begin{align}
B_\text{lost}(\mathcal{E},\hat\rho) = S(\hat\rho) - \mathcal{C}(\mathcal{E}).
\end{align}
Then there are two cases to consider -- upper and lower bounds on accumulated lost bits.

The best-case scenario is that subsequent channels lose the same bits, giving us a lower bound on the number of lost bits as the maximum number of bits lost by the constituent channels,
\begin{align}
B_\text{lower}(\mathcal{E}_2\circ\mathcal{E}_1,\hat\rho) = \text{max}[B_\text{lost}(\mathcal{E}_1,\hat\rho), B_\text{lost}(\mathcal{E}_2,\hat\rho)].
\end{align}
Alternately, each subsequent channel could lose a different set of bits, in which case the number of lost bits accumulates additively,
\begin{align}
B_\text{upper}(\mathcal{E}_2\circ\mathcal{E}_1,\hat\rho) = B_\text{lost}(\mathcal{E}_1,\hat\rho) + B_\text{lost}(\mathcal{E}_2,\hat\rho). 
\end{align}
Then, the number of actual bits lost is bounded from above and below as,
\begin{align}
B_\text{lower} \leq B_\text{lost} \leq B_\text{upper}.	
\end{align}

%In the case of mutual information, which is not a metric, one can use it to define the \textit{variation of information} metric,
%\begin{align}\index{Variation of information}
%d_\text{VI}(X,Y) &= H(X,Y) - I(X;Y), \nonumber \\
%d_\text{VI}(\hat\rho_A,\hat\rho_B) &= S(\hat\rho_A,\hat\rho_B) - I(\hat\rho_A;\hat\rho_B),
%\end{align}
%or for a channel,
%\begin{align}
%d_\text{VI}(\hat\rho,\mathcal{E}) &= S(\hat\rho,\mathcal{E}(\hat\rho)) - I(\hat\rho;\mathcal{E}(\hat\rho)),
%\end{align}
%which obeys the metric properties.

>>>>

The efficiency measure introduced previously is multiplicative, so for consecutive lossy channels the net efficiency is,
\begin{align}
\eta_\mathrm{net}=\prod_i \eta_i,
\end{align}
where $\eta_i$ is the efficiency of the $i$th channel. Intuitively, this is simply telling us that if a photon passes through a channel with success probability $\eta_1$, followed by another with $\eta_2$, the total success probability is \mbox{$\eta_1\eta_2$}.

When employing single-photon encoding of qubits (e.g using the polarisation degree of freedom), there are three basis states of interest: a single photon horizontally polarised ($\ket{H}$); a single photon vertically polarised ($\ket{V}$); and, the vacuum state ($\ket{0}$). The effect of the loss channel on this type of state is to map $\ket{H}$ and $\ket{V}$ to $\ket{\mathrm{0}}$ with probability \mbox{$1-\eta$}, while doing nothing to $\ket{\mathrm{0}}$. Note that because the loss process affects both logical basis states ($\ket{H}$ and $\ket{V}$) identically, its action is invariant under unitary operations in the logical (i.e polarisation) basis space.

@@

Because spectral filtering can be regarded as a frequency-dependent loss channel, its associated cost can be treated in the same manner, except that rather than keeping track of a single efficiency $\eta$, we track a frequency response function $\eta_f(\omega)$, with the same multiplicative property,
\begin{align}
	\eta_f^\mathrm{(net)}(\omega)=\prod_i \eta_f^{(i)}(\omega).
\end{align}

@@

The dephasing and depolarising channels, given by Eqs.~(\ref{eq:dephasing_channel},\ref{eq:depolarizing_channel}), also behave multiplicatively. If $p_i$ is the probability that the state passing through the $i$th channel in series does not undergo the error process, then the probability of the state passing though the entire series without error is simply,
\begin{align}
p_\mathrm{net}=\prod_i p_i,
\end{align}
exhibiting the same multiplicative behaviour as the loss channel. The same observation applies to any of the other Pauli error channels.

@@

In Sec.~\ref{sec:MM_error} we introduced a simple model for temporal mode-mismatch as a displacement in the temporal wave-function of photons propagating through a channel. Clearly, such a process is cumulative -- a temporal displacement of $\Delta_1$ followed by another of $\Delta_2$ yields a net displacement of \mbox{$\Delta_1+\Delta_2$}. Thus, for a chain of such channels we simply accumulate a net temporal displacement of,
\begin{align}
\Delta_\mathrm{net} = \sum_i \Delta_i.
\end{align}

@@

The fidelity\index{Fidelity} between two states is defined as,
\begin{align}
\mathcal{F}(\hat\rho_1,\hat\rho_2) = \mathrm{tr}\left(\sqrt{\hat\rho_1^{1/2}\cdot\hat\rho_2\cdot\hat\rho_1^{1/2}}\right),
\end{align}
where,
\begin{align}
& \mathcal{F}(\hat\rho_1,\hat\rho_2) = \mathcal{F}(\hat\rho_2,\hat\rho_1), \nonumber \\
& 0\leq \mathcal{F}(\hat\rho_1,\hat\rho_2) \leq 1.
\end{align}
\mbox{$\mathcal{F}(\hat\rho_1,\hat\rho_2)=1$} iff the states are equal, and \mbox{$\mathcal{F}(\hat\rho_1,\hat\rho_2)=0$} iff they are orthogonal.
In the case where one of the states is a pure state, this simplifies to,
\begin{align}
\mathcal{F}(\hat\rho_1,\ket{\psi_2}) = \bra{\psi_2}\hat\rho_1\ket{\psi_2},
\end{align}
and when both states are pure to simply,
\begin{align}
\mathcal{F}(\ket{\psi_1},\ket{\psi_2}) = |\langle\psi_1 | \psi_2\rangle|^2.
\end{align}

@@

We define the fidelity of two processes, the process fidelity \index{Fidelity} \cite{bib:Gilchrist05}, to be the fidelity between two identical copies of a state that have been evolved under each of those processes, minimised over all possible states. That is, it provides a lower bound on the fidelity between identical states evolved under the two processes. In the context of networking, where quality must be guaranteed, this definition is more appropriate than, say, the average case fidelity. Specifically,
\begin{align}
\mathcal{F}(\mathcal{E}_1,\mathcal{E}_2) = \mathrm{tr}\left( \sqrt{\chi_1^{1/2}\cdot\chi_2\cdot\chi_1^{1/2}}\right),
\end{align}
where $\chi_1$ and $\chi_2$ are the process matrices for $\mathcal{E}_1$ and $\mathcal{E}_2$.

@@

The purity of a state that was initially pure quantifies how well quantum coherence was maintained during evolution, equivalently how well superpositions are maintained. The purity is defined as,
\begin{align}
\mathcal{P}(\hat\rho) = \mathrm{tr}(\hat\rho^2),
\end{align}
where,
\begin{align}
\frac{1}{\mathrm{dim}(\hat\rho)} \leq \mathcal{P}(\hat\rho) \leq 1.
\end{align}
We have \mbox{$\mathcal{P}(\hat\rho) = 1$} iff \mbox{$\hat\rho=\ket{\psi}\bra{\psi}$} is a pure state, and \mbox{$\mathcal{P}(\hat\rho)=1/\mathrm{dim}(\hat\rho)$} iff \mbox{$\hat\rho=\mathbb{\hat{I}}/\mathrm{dim}(\hat\rho)$} is the maximally mixed state.

@@

The purity of a process is defined analogously to the fidelity of a process,
\begin{align}
\mathcal{P}(\mathcal{E}) = \mathrm{tr}(\chi^2),
\end{align}
and as with the fidelity, a lower bound on the purity of multiple processes in series is multiplicative,
\begin{align}
\mathcal{P}(\mathcal{E}_2\circ\mathcal{E}_1)
\geq \mathcal{P}(\mathcal{E}_2)\cdot\mathcal{P}(\mathcal{E}_1).
\end{align}
\comment{CHECK THIS!}. If the channel implements a unitary operation then necessarily \mbox{$\mathcal{P}(\mathcal{E})=1$}.

@@

When distributing entanglement between separate nodes, metrics quantifying bipartite entanglement are relevant. For pure bipartite states $\ket{\psi}_{A,B}$, the purity of one of the reduced subsystems directly quantifies the degree of entanglement between them,
\begin{align}
\mathcal{M}(\ket{\psi}_{A,B})) &= \mathcal{P}(\mathrm{tr}_A(\ket{\psi}_{A,B})) \nonumber \\
&= \mathcal{P}(\mathrm{tr}_B(\ket{\psi}_{A,B})),
\end{align}
The entanglement between two systems in invariant under local unitaries,
\begin{align}
\mathcal{M}(\ket{\psi}_{A,B}) = \mathcal{M}([\hat{U}_A\otimes \hat{U}_B]\ket{\psi}_{A,B}).
\end{align}

@@

The Shannon entropy \cite{???} of a classical probability distribution $X$ is given by,
\begin{align}\index{Shannon entropy}
H(X) = -\sum_x p_x\mathrm{log}_2(p_x),
\end{align}
where $p_x$ are the probabilities in the distribution. For a joint distribution over $X$ and $Y$ this simply generalises to,
\begin{align}\index{Joint Shannon entropy}
H(X,Y) =  -\sum_{x,y} p_{x,y}\mathrm{log}_2(p_{x,y})
\end{align}

The von Neuman entropy \cite{???} for quantum density operators, $S(\hat\rho)$, is defined analogously, replacing probabilities with density operator eigenvalues,
\begin{align}\index{von Neuman entropy}
S(\hat\rho) &= - \sum_x \lambda_x \mathrm{log}_2 (\lambda_x) \nonumber \\
&= -\mathrm{tr}(\hat\rho\,\mathrm{log}\,\hat\rho),
\end{align}
where $\{\lambda\}$ is the eigenvalue spectrum of $\hat\rho$. This modification is logically justified, as the eigenvalues can be interpreted directly as a purely classical probability distribution of orthogonal states when the density operator is transformed into a basis with no coherences between basis states (i.e a diagonal basis or spectral decomposition). In that case the Shannon and von Neuman entropies essentially have identical physical interpretations.

@@

In general, for a series of links \mbox{$v_1\to v_2 \to \dots \to v_n$} characterised by multiplicative measure $m$, the equivalent cost metric is,
\begin{align} \label{eq:dist_log}\index{Logarithmic distance}
c_{v_1\to v_2 \to \dots \to v_n} = -\sum_{i=1}^{n-1} \mathrm{log}(m_{v_i\to v_{i+1}}).
\end{align}
We have assumed that \mbox{$0\leq m \leq 1$}, where \mbox{$m=0$} represents complete failure, and \mbox{$m=1$} represents ideal operation.

@@

In the case of mutual information and channel capacity, it makes most sense to consider the number of bits that are lost by a channel, rather than the number communicated, since then we have a measure with quasi-metric properties. Specifically, let the number of bits lost by a channel be the difference between the number of bits in the input state and the channel capacity,
\begin{align}
B_\mathrm{lost}(\mathcal{E},\hat\rho) = S(\hat\rho) - \mathcal{C}(\mathcal{E}).
\end{align}
Then there are two cases to consider -- upper and lower bounds on accumulated lost bits.

The best-case scenario is that subsequent channels lose the same bits, giving us a lower bound on the number of lost bits as the maximum number of bits lost by the constituent channels,
\begin{align}
B_\mathrm{lower}(\mathcal{E}_2\circ\mathcal{E}_1,\hat\rho) = \mathrm{max}[B_\mathrm{lost}(\mathcal{E}_1,\hat\rho), B_\mathrm{lost}(\mathcal{E}_2,\hat\rho)].
\end{align}
Alternately, each subsequent channel could lose a different set of bits, in which case the number of lost bits accumulates additively,
\begin{align}
B_\mathrm{upper}(\mathcal{E}_2\circ\mathcal{E}_1,\hat\rho) = B_\mathrm{lost}(\mathcal{E}_1,\hat\rho) + B_\mathrm{lost}(\mathcal{E}_2,\hat\rho). 
\end{align}
Then, the number of actual bits lost is bounded from above and below as,
\begin{align}
B_\mathrm{lower} \leq B_\mathrm{lost} \leq B_\mathrm{upper}.	
\end{align}

%In the case of mutual information, which is not a metric, one can use it to define the \textit{variation of information} metric,
%\begin{align}\index{Variation of information}
%d_\mathrm{VI}(X,Y) &= H(X,Y) - I(X;Y), \nonumber \\
%d_\mathrm{VI}(\hat\rho_A,\hat\rho_B) &= S(\hat\rho_A,\hat\rho_B) - I(\hat\rho_A;\hat\rho_B),
%\end{align}
%or for a channel,
%\begin{align}
%d_\mathrm{VI}(\hat\rho,\mathcal{E}) &= S(\hat\rho,\mathcal{E}(\hat\rho)) - I(\hat\rho;\mathcal{E}(\hat\rho)),
%\end{align}
%which obeys the metric properties.
